Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-17 arxiv-version/np-hardness-of-the-weak-labeling-problem.tex
minor edits in arxiv version
Unify bibfiles

The hardness proof is based on a reduction from the set splitting problem, which is proven to be NP-complete by Lovasz \cite{garey1979computers}, to our weak labeling problem. The reduction is adapted from \cite{blum1989training}. 
\begin{figure}[h]
\begin{framed}
\begin{center}
    \textbf{Set Splitting}
\end{center}
\textbf{Given: } A finite set $S$ and a collection $C$ of subsets $c_i$ of $S$. \\
\textbf{Question: } Do there exist disjoint sets $S_1$ and $S_2$ such that $S_1 \cup S_2 = S$ and $\forall i, c_i\not\subseteq S_1$ or $c_i\not\subseteq S_2$? 
\end{framed}
\end{figure}

@@

 Now we show $\forall j$, $c_j \not\subset S_1$ and $c_j \not\subset S_2$ by contraction. Assume there exists some $j$ such that $c_j \subset S_1$. By our definition of $S_1$, we have $\ip{w_1-w_3}{(\e_i, 1)} > 0$ for all $i\in c_j$. Therefore, 
 \begin{align*}
     \sum_{i\in c_j}\ip{w_1-w_3}{\left(\e_i, 1\right)} = \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, |c_j|\right)} > 0. 
 \end{align*}
 Because Type 1 sample has label $3$, we also have
 \begin{align*}
     \ip{w_1-w_3}{\left(\zero, 1\right)} < 0. 
 \end{align*}
 Combining the above two inequalities, we get
 \begin{align*}
     \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, 1\right)} = \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, |c_j|\right)} - (|c_j|-1)\ip{w_1-w_3}{\left(\zero, 1\right)}>0.  
 \end{align*}
 Note that $\left(\sum_{i\in c_j}\e_i, 1\right)$ is a feature vector for Type 3 samples. Thus the above inequality contradicts that Type 3 samples have label 3. Therefore, $c_j \subset S_1$. If we assume there exists some $c_j \not\subset S_2$, same arguments apply and also lead to contradiction. 
\end{proof}

>>>>

The hardness proof is based on a reduction from the set splitting problem, which is proven to be NP-complete by Lovasz \cite{Garey-Johnson-1979}, to our weak labeling problem. The reduction is adapted from \cite{Blum-Rivest-1993}. 
\begin{figure}[h]
\begin{framed}
\begin{center}
    \textbf{Set Splitting}
\end{center}
\textbf{Given: } A finite set $S$ and a collection $C$ of subsets $c_i$ of $S$. \\
\textbf{Question: } Do there exist disjoint sets $S_1$ and $S_2$ such that $S_1 \cup S_2 = S$ and $\forall i, c_i\not\subseteq S_1$ or $c_i\not\subseteq S_2$?
\end{framed}
\end{figure}

@@

 Now we show $\forall j$, $c_j \not\subset S_1$ and $c_j \not\subset S_2$ by contraction. Assume there exists some $j$ such that $c_j \subset S_1$. By our definition of $S_1$, we have $\ip{w_1-w_3}{(\e_i, 1)} > 0$ for all $i\in c_j$. Therefore,
 \begin{align*}
     \sum_{i\in c_j}\ip{w_1-w_3}{\left(\e_i, 1\right)} = \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, |c_j|\right)} > 0.
 \end{align*}
 Because Type 1 sample has label $3$, we also have
 \begin{align*}
     \ip{w_1-w_3}{\left(\zero, 1\right)} < 0.
 \end{align*}
 Combining the above two inequalities, we get
 \begin{align*}
     \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, 1\right)} = \ip{w_1-w_3}{\left(\sum_{i\in c_j}\e_i, |c_j|\right)} - (|c_j|-1)\ip{w_1-w_3}{\left(\zero, 1\right)}>0.
 \end{align*}
 Note that $\left(\sum_{i\in c_j}\e_i, 1\right)$ is a feature vector for Type 3 samples. Thus the above inequality contradicts that Type 3 samples have label 3. Therefore, $c_j \not\subset S_1$. If we assume there exists some $c_j \subset S_2$, same arguments apply and also lead to contradiction.
\end{proof}
